Deriving Random Generators via\\ Higher-Level Representations

### 2019-01-23 paper/abstract.tex
Abstract

  Pellentesque dapibus suscipit ligula. Donec posuere augue in quam. Etiam vel
  tortor sodales tellus ultricies commodo. Suspendisse potenti. Aenean in sem ac
  leo mollis blandit. Donec neque quam, dignissim in, mollis nec, sagittis eu,
  wisi. Phasellus lacus. Etiam laoreet quam sed arcu. Phasellus at dui in ligula
  mollis ultricies. Mauris mollis tincidunt felis. Aliquam feugiat tellus ut
  neque. Nulla facilisis, risus a rhoncus fermentum, tellus tellus lacinia
  purus, et dictum nunc justo sit amet elit.

>>>>

  % Status
  Automatic generation of random values described by abstract data types (ADTs)
  is often a hard task.
  % data types (ADTs), % ---specially when considering ADTs which
  % represent HTML pages, images, programs or other structural rich objects.
  % Situation
  State-of-the-art random testing tools often can automatically synthesize
  random data generators based on ADTs definitions.
  %
  In that manner, generated values comply with the structure described by
  ADTs---something that proves useful when testing software which expects
  complex input like web pages, images, or even programs.
  %
  % Problem
  However, it sometimes becomes necessary to generate structural richer ADTs
  values in order to test deeper software layers.
  %
  % Solution
  In this light, we propose to leverage static information found in the
  codebase as a manner to improve the generation process.
  %
  Namely, our generators are capable to consider how programs branch on input
  data as well as how ADTs values are built via interfaces.
  %
  % Concretely, we propose to consider not only ADTs definitions, but also how
  % programs branch on input data as well as how ADTs values get manipulated via
  % interfaces.
  %
  We implement a tool, called {\dragenp}, responsible to synthezise generators
  for ADTs values while providing compile-time guarantees about their
  distributions.
  %
  Our compile-time predictions allow {\dragenp} to provide an heuristic that
  tries to adjust the distribution of generators to what developers might want.
  \todo[inline,author=Ale]{Case study}
